On Secure Delegation of SampBQP with a Classical Client

### 2020-01-05 privacy.tex
Fix typo

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
			\begin{itemize}
				\item $\lambda$: security parameter
				\item $L$: maximum size of circuits that can be homomorphically evaluated
			\end{itemize}
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
			\begin{itemize}
				\item $f$: a circuit of depth at most $L$
				\item Satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_1),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$
			\end{itemize}
	\end{itemize}
\end{dfn}

Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.

>>>>

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
			\Ethan{Urmila didn't specify that $\mathsf{Dec}\circ\mathsf{Enc}=Id$}
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

Everything also has an implicit dependence on $1^L$, where $L$ is the maximum circuit depth for the homomorphic evaluation.
As this is a homomorphic encryption scheme, it satisfies $$\mathsf{HE.Dec}_{sk}(c_f)=f(\mathsf{HE.Dec}_{sk}(c_0),\ldots,\mathsf{HE.Dec}_{sk}(c_l))$$ with all but negligible probability in $\lambda$
